%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a4paper,10pt]{article} % Default font size and paper size

\usepackage{fontspec} % For loading fonts
\defaultfontfeatures{Mapping=tex-text}

\usepackage{url,parskip, xspace} % Formatting packages

\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors

%\usepackage[big]{layaureo} % Margin formatting of the A4 page, an alternative to layaureo can be usepackage{fullpage}
% To reduce the height of the top margin uncomment: \addtolength{\voffset}{-1.3cm}
\usepackage{fullpage}

\usepackage{hyperref} % Required for adding links	and customizing them
\definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{3pt}{3pt} % Spacing around sections

\begin{document}

\pagestyle{empty} % Removes page numbering

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\par{\centering{\Huge Shayan \textsc{Doust}}\bigskip\par} % Your name

\section{Personal Data}

\begin{tabular}{rl}
\textsc{Location:} & Liverpool, United Kingdom \\
\textsc{Date of Birth:} & 03 October 2000 \\
\textsc{Phone:} & 07419767775\\
\textsc{LinkedIn:} & \href{https://www.linkedin.com/in/shayan-doust/}{https://www.linkedin.com/in/shayan-doust/} \\
\textsc{email:} & \href{mailto:hello@shayandoust.me}{hello@shayandoust.me} \\
\end{tabular}

%----------------------------------------------------------------------------------------
%	PERSONAL STATEMENT
%----------------------------------------------------------------------------------------

\section{Personal Statement}

I am a studious and persevering student studying \textbf{MSc Theoretical Computer Science} at the \textit{University of Liverpool}. Having attained a $1^{st}$ class Honours in \textbf{BSc Computer Science} specialising in Artificial Intelligence \& Machine Learning, I am looking to pursue my ambition of enrolling in a PhD programme  in a related field. I enjoy Mathematics; particularly, I take joy in reading past and recent theoretical publications and assessing how I can build upon it. With a high achievement at University and my work in providing a net business value as a Data Scientist at GlaxoSmithKline, I strive to push myself to be in the frontier of prospective research. 

%----------------------------------------------------------------------------------------
%	EDUCATION & WORK
%----------------------------------------------------------------------------------------

\section{Education \& Work}

\begin{tabular}{rl}	
\textsc{September} 2023 - \textsc{Present} & \textbf{University of Liverpool} \\
&\normalsize \textsc{MSc Theoretical Computer Science} \\
&\normalsize Current modules include Multi-Agent Reinforcement Learning \\
& and Distributed Systems. \\
&\\
%------------------------------------------------
\textsc{September} 2019 - \textsc{September} 2023 & \textbf{University of Liverpool} \\
&\normalsize \textsc{BSc Computer Science with a year in industry} \\
& \\
&\normalsize Artificial Intelligence/Machine Learning specialty pathway. \\
&\textsc{ACHIEVED 1\textsuperscript{st} class Honours.} \\
&\\
%------------------------------------------------

\textsc{August} 2021 - \textsc{August} 2022 & \textbf{GlaxoSmithKline Industrial Placement} \\
&\normalsize Worked as a Data Scientist in a strictly-agile environment \\
& within the domain of Pharmaceuticals. Responsibilities \\
& included the strategic unification of keyless data in our \\
& Apache Hadoop clusters, visualisation of data landscape \\
& using R, and the computer vision centric quality control \\
& of pseudocoloured chromosome masks from our \\
& in-vitro pipeline. \\
&\\
%------------------------------------------------

\textsc{September} 2017 - \textsc{2019} & \textbf{Upton by Chester high school} \\
&\normalsize \textit{3 A-Levels: Maths, Physics \& Computer Science} \\
&\\
&\textsc{ACHIEVED A* - C} \\
&\normalsize \textit{A-Level project:} cross-platform encrypted messaging application \\
& in C/C++ \\
&\\
%------------------------------------------------

\textsc{September} 2016 - \textsc{2017} & \textbf{Upton by Chester high school} \\
&\normalsize \textit{6 GCSEs including Maths, Physics \& Computer Science}
%------------------------------------------------

\end{tabular}

%----------------------------------------------------------------------------------------
%	SKILLS 
%----------------------------------------------------------------------------------------

\section{Skills}

\begin{itemize}
\item{\textbf{Expert understanding of *nix systems.}} \\
11 years of using Unix-like systems such as GNU/Linux. Additionally, worked with and compiled several softwares for packages on various architectures such as Arm, Amd64, Mips, et cetera.
\item{\textbf{Data scraping, wrangling, modeling and evaluation.}} \\
I further strengthened these skills by pursuing the Data Science professional certificate on edX as well as using internet resources to teach myself. I am particularly excited as Data Science \& Artificial Intelligence is my chosen module for this year's university.
\item{\textbf{Knowledge of R statistical language, Java, Python and C(++).}} \\
R language has been used when learning about statistics. I have also trialled with using Rcpp to write R modules.
\item{\textbf{Understanding of algorithmic methods of optimisation.}}
\item{\textbf{Strong experience with cloud services like AWS and Google Cloud Compute.}}
\item{\textbf{Strong experience with DataBricks and general Apache Spark platforms.}}
\item{\textbf{Proficient with writing and delivering complex models through popular AI/ML frameworks like TensorFlow.}}
\item{\textbf{Interpersonal skills with the ability to orchestrate and lead groups.}}
\item{\textbf{Strong experience with using Conda environment, more specifically Bioconda.}}
\item{\textbf{Comfortable with formulating and working with common statistical \\ methodologies such as p-values, linear regression, probability, Bayes' theorem and multivariate modelling.}}
\item{\textbf{A critical thinker.}}
\item{\textbf{Passion of learning and gaining a deeper understanding of concepts.}}
\item{\textbf{High social understanding \& eager to help others.}}
\item{\textbf{First experiences with forcasting and predictive models.}} \\
Practised using the datasets within the \href{https://cran.r-project.org/web/packages/dslabs/index.html}{dslabs} package.
\item{\textbf{Great communicative skills.}} \\
Confidence and ability to converse within teams during teamworks, or to address a wider audience.
\item{\textbf{Ability to deliver qualitative and quantitative work under heavy workload, time constraints and pressure.}} \\
I am able to formulate a mental work-time structure in order to fairly and efficiently balance work to prevent any sort of bottlenecking.
\end{itemize}

%----------------------------------------------------------------------------------------
%	NOTABLE CERTIFICATES & ACHIEVEMENTS
%----------------------------------------------------------------------------------------

\section{Achievements \& Certificates}

\begin{tabular}{rl}
\textsc{July} 2020 & Attained the \textbf{\href{https://credentials.edx.org/credentials/bf98d6fd623848c184c1ba57829d6b64/}{Data Science professional certificate}}\\ 
\footnotesize(\textbf{HarvardX $@$ edX})\normalsize\\
\textsc{May} 2019 - \textsc{August} 2022 & \href{https://qa.debian.org/developer.php?login=hello%40shayandoust.me}{Debian maintainer} and prospective developer within the Debian-Med team \normalsize\\
\end{tabular}
\\\\\\
The Data Science certificate I have attained acts as a major supplement to my A.I. and analytics module I took during my Undergraduate course. They both fairly overlap and this has helped fill any void in my knowledge.
%----------------------------------------------------------------------------------------
%	INTERESTS
%----------------------------------------------------------------------------------------

\section{Interests}

Desire and motivation of exploring and self-teaching new elements within the field of Data Science \& Machine Learning, as well as mathematical theorems in the realm of Artificial Intelligence; my BSc honour's project was based on the design and implementation of a pipeline that takes in noisy MRI images as input, and outputs clean MRI images segmenting any benign and malignant tumours present - achieved 80\% Jaccard similarity.

\end{document}